---
title: "Final Project 2"
author: "Ngun Tial"
date: "2024-02-20"
output:
  html_document: default
  pdf_document: default
toc: yes
---
## Introduction

This report analyzes the `ocd_patient_dataset.csv` dataset, which contains information on demographic details, clinical information, symptom severity, co-occurring mental health conditions, medication history, and family history of patients diagnosed with Obsessive-Compulsive Disorder (OCD). The objectives of this analysis are:

- Explore the demographic characteristics of OCD patients
- Analyze the demographic and duration of symptoms, obsession type, and compulsive type
- Identify if there are any patterns or trends in certain ethnicities or family history of OCD

## Data Loading

```{r, read-data-from-local_directory, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
ocd_data <- read_csv("~/Downloads/final_project/data/ocd_patient_dataset.csv")
```

## Demographic Characteristics
This table provides insights into the education level reported by individuals of different ethnicity within the OCD patient dataset. 

```{r, demographic table, echo=FALSE}
library(knitr)
# Combine tables for demographic characteristics
Demographics_Table <- cbind(
  Gender = table(ocd_data$Gender),
  Ethnicity = table(ocd_data$Ethnicity),
  `Marital Status` = table(ocd_data$`Marital Status`),
  `Education Level` = table(ocd_data$`Education Level`)
)

# Convert table to data frame
Demographics_Table_df <- as.data.frame(Demographics_Table)

# Display the table using kable
kable(Demographics_Table_df, caption = "Table 1: Demographic Characteristics of OCD Patients")
```

## Graph 
Analyze the relationship between demographic factors, duration of symptoms, OCD types, and severity

```{r, echo=FALSE}
library(ggplot2)

# Create a combined boxplot
ggplot_data <- ggplot(ocd_data, aes(x = Gender, y = `Duration of Symptoms (months)`, fill = Gender)) +
  geom_boxplot() +
  labs(title = "Relationship between Gender and Duration of Symptoms",
       x = "Gender",
       y = "Duration of Symptoms (months)") +
  theme_minimal() +
  facet_wrap(~ `Obsession Type`, scales = "free", ncol = 2) +
  geom_boxplot(aes(x = `Obsession Type`, y = `Y-BOCS Score (Obsessions)`, fill = `Obsession Type`), position = "dodge", alpha = 0.7) +
  labs(title = "Relationship between Obsession Type and Y-BOCS Score",
       x = "Obsession Type",
       y = "Y-BOCS Score (Obsessions)") +
  geom_boxplot(aes(x = `Compulsion Type`, y = `Y-BOCS Score (Compulsions)`, fill = `Compulsion Type`), position = "dodge", alpha = 0.7) +
  labs(title = "Relationship between Compulsion Type and Y-BOCS Score",
       x = "Compulsion Type",
       y = "Y-BOCS Score (Compulsions)") +
  theme(legend.position = "bottom")
print(ggplot_data
      )
```











