---
title: "Final Project 2"
author: "Ngun Tial"
date: "2024-02-20"
output:
  pdf_document: default
  html_document: default
toc: yes
---
## Introduction

This report analyzes the `ocd_patient_dataset.csv` dataset, which contains information on demographic details, clinical information, symptom severity, co-occurring mental health conditions, medication history, and family history of patients diagnosed with Obsessive-Compulsive Disorder (OCD). The objectives of this analysis are:

- Explore the demographic characteristics of OCD patients
- Analyze the demographic and duration of symptoms, obsession type, and compulsive type
- Identify if there are any patterns or trends in certain ethnicities or family history of OCD

## Data Loading
```{r, here-i-am, include = FALSE}
here::i_am(
  "report.rmd")
```


## Demographic Characteristics
This table provides insights into the education level reported by individuals of different ethnicity within the OCD patient dataset. 

```{r, demographic table, echo=FALSE}
# Combine tables for demographic characteristics
readRDS(
  here::here("output/Demographics_Table.rds")
  )
```

## Graphical Analysis 
Analyze the relationship between demographic factors, duration of symptoms, OCD types, and severity

```{r, echo=FALSE}
#| fig.align = "center",
#| out.width = "600px"
library(knitr)
knitr::include_graphics(
  here::here("output/ggplot_data.png")
  )

knitr::include_graphics(
  here::here("output/obsession_duration.png")
  )

knitr::include_graphics(
  here::here("output/compulsion_duration.png")
  )

knitr::include_graphics(
  here::here("output/compulsion_severity.png")
  )

knitr::include_graphics(
  here::here("output/obsession_severity.png")
  )
```












